yield response function

### 2025-08-24 codes/R/visualized_results.qmd
comparison plot added

>>>>

# comparison plot

```{r}
# compare to which model?
baseline <- "NO_RF"

# average RMSE by Model × field
avg_by <- rmse_df %>%
  dplyr::group_by(Model, field_f) %>%
  dplyr::summarise(mean_rmse = mean(RMSE), .groups = "drop")

# baseline per field 
baseline_by_field <- avg_by %>%
  dplyr::filter(Model == baseline) %>%
  dplyr::select(field_f, baseline_rmse = mean_rmse)

# join and compute % improvement
rel <- avg_by %>%
  dplyr::left_join(baseline_by_field, by = "field_f") %>%
  dplyr::filter(!is.na(baseline_rmse)) %>%
  dplyr::mutate(
    pct_impr = 100 * (baseline_rmse - mean_rmse) / baseline_rmse
    # or: pct_impr = (1 - mean_rmse / baseline_rmse) * 100
  ) %>%
  dplyr::filter(Model != baseline)

# Plot
library(ggplot2)
p_rel <- ggplot(rel, aes(x = field_f, y = pct_impr, fill = Model)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.65) +
  geom_hline(yintercept = 0, linewidth = 0.4) +
  geom_text(aes(label = sprintf("%.1f%%", pct_impr)),
            position = position_dodge(width = 0.7), vjust = -0.4, size = 3, show.legend = FALSE) +
  scale_y_continuous(expand = expansion(mult = c(0.02, 0.10))) +
  labs(x = "# fields", y = sprintf("Improvement vs %s (%%)", baseline), fill = "Model") +
  theme_bw()

p_rel
